\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-11 paper.tex
Modify descryption

\maketitle
\section*{\normalsize\textbf{Abstract}}
Data as a Service (DaaS) has been offering consumption data, geographic information, etc., for a number of years and has evolved into a multi-billion dollar industry. But IoT cannot be considered a mere extension of DaaS. Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled data marketplaces, trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.

In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, posting the trade records but also including the transaction process on the distributed ledgers. This way can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain. In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of the device, simultaneously making a verifiable Auth-compliant request to the platform. Later, the verified data will enter the data marketplace to be traded. Furthermore, the platform will complete matching, trading and refunding process without the human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.

@@

The sustainability of IoT economic system is under discussion by Dusit Niyato et al.\cite{UtilityStruct}. They evaluated the utility structure of data trading and presented game theory model with the utility structure which provides a way to find out the Nash Equilibrium. The existence of Nash Equilibrium can help us to determine if the policy of the decentralized data marketplace can ensure a sustainable system. However, few things didn't be mentioned in their work including refund and subscription economy.

@@

\section{\normalsize\textbf{Trading Model}}
In the following, we describe the data trading process in detail. To participate a data marketplace, data providers and consumers have to register first. Then data provider can launch its product on the marketplace. Once a product is launched, it is searchable and could be traded afterward. The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.

@@

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys. Only one Registration Contract is needed, and everyone can query the participants' public keys. Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications. After that, their identities are available in the Registration Contract and launching and trading processes can be started.

@@

\subsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaciton among game players. If we can ensure Nash Equilibrium of decentralized data marketplace exists at certain acceptable range, then we can promise the sustainability of decentralized data marketplace. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied on data pricing. To describe the scenario more precisely, we decided to use repeated game to build our game theory model which meets the scenario of subscription economy more.

@@

\begin{figure} \centering \includegraphics[width=3.3in]{decision_tree} \caption{Decision Tree}
    \label{fig:decision_tree} \end{figure}
For every $n$ round, the data provider would cost $C_{maintain}$ to maintain or enhance the sensors that data provider owns. We call this as a maintain period. Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discounted factor $\beta$ to depict this phenomena.

We have these following assumptions:
\begin{itemize}
    \item  There is no any other data providers provide the same product in Data Marketplace. Therefore, we can consider each provider's behavior independently. That means this decision tree represent the behavior of only one data provider.
    \item  More than 51\% of consumers are among complete information exchange state. In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
    \item  One of the consumers who has complete information exchange with other 51\% buyers has the ability to examine the data quality. If unacceptably low accuracy data are delivered to consumers, this examiner will spread this information out.
    \item  We assume the number of dishonest consumers is really small, so it can be negleted.
\end{itemize}

@@

Al-Fagih et al. presented\cite{DataPrice} $P_s$ is sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$. We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq. (\ref{payoff}), then we can find out the Nash Equilibrium of repeated game. We will discuss more in the next section.

@@

\section{\normalsize\textbf{Future Work}}
%Data Auction
The data auction process is a data trading mechanism and an economically-driven scheme that establishes corresponding prices of data products through bidding process between consumers and providers. While there has been many auction models\cite{BigPicDataMarket} in several areas, only a few of research focus on third-party auction platform. Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers. However, the auction process between multiple participants and analyzing potential threats are still critical issues that need to be resolved.

>>>>

\maketitle
\section*{\normalsize\textbf{Abstract}}
Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and has come to form a multi-billion dollar industry. But IoT cannot be considered a mere extension of DaaS. Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled Data Marketplaces, trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.

In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, putting not merely the trading records but also the transaction process on the distributed ledgers. This way can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain. In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of device, simultaneously making a verifiable Auth-compliant request to the platform. Later, the verified data will enter data marketplace to be traded. Furthermore, the platform will complete matching, trading and refunding without human intervention in the whole process, and also protect the rights of data providers and consumers through trading policy written on smart contract, and finally apply evolutionary game theory to machine economy.

@@

The sustainability of IoT economic system is under discussion by Dusit Niyato et al.\cite{UtilityStruct}. They evaluated the utility structure of data trading and presented game theory model.  Data marketplace organizers can determine their policies to ensure a sustainable system with the Nash Equilibrium found by game theory and the utility structure. However, refund and subscription economy were not mentioned in their work.

@@

\section{\normalsize\textbf{Trading Model}}
In the following, we describe the data trading process in detail and we would use game theory to ensure the sustainability of our tading model. To participate a data marketplace, data providers and consumers have to register first. Then data provider can launch its product on the marketplace. Once a product is launched, it is searchable and could be traded afterward. The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.

@@

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys. Only one Registration Contract is needed, and everyone can query the participants' public keys. Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications. After that, their identities are available in the Registration Contract and launching and trading processes can be started.

@@

\subsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaciton among game players. If we can ensure Nash Equilibrium of decentralized data marketplace exists at certain acceptable range, then we can promise the sustainability of decentralized data marketplace. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied on data pricing. We choose repeated game to build our game theory model. Repeated game consists of several repetitions of the same base game which meets the scenario of data subscription.

@@

\begin{figure} \centering \includegraphics[width=3.3in]{decision_tree} \caption{Decision Tree}
    \label{fig:decision_tree} \end{figure}
For every $n$ round, the data provider would pay $C_{maintain}$ to enhance the sensors that data provider owns. We call this as a maintain period. Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discounted factor $\beta$ to depict this phenomena.

We have these following assumptions:
\begin{enumerate}
    \item  We assume consumers are rational. \label{rational_man}
    \item  Each data provider monopoly of the product they produced. \label{monopoly}
    \item  Subscription fee only depends on data quality. \label{fee_vs_quality}
    \item  At least 51\% of consumers are in the same group which has complete information exchange.\label{51_in_group} 
    \item  One of the consumers who has complete information exchange with other 51\% buyers has the ability to examine the data quality. \label{1_in_51}
\end{enumerate}

According to \textbf{assumption(\ref{rational_man})}, we learn that few consumers would take malicious actions in this system, since all the consumers are rational.

\textbf{Assumption(\ref{monopoly})} implies there is no other data providers provide the same product in Data Marketplace. In this way, we can consider each provider's behavior independently. That means this decision tree represent the behavior of only one data provider.

From \textbf{assumption(\ref{51_in_group})}, we derive one thing that once one of any consumer in that group launches voting for stopping buying data (in other words, the comsumer annonces the data quality is not acceptable), they would succeed in rejecting the processing subscription.

\textbf{Assumption(\ref{1_in_51})}  implies if unacceptably low accuracy data are delivered to consumers, the examiner will spread this information out.

@@

Al-Fagih et al. presented\cite{DataPrice} $P_s$ is sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$. We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq. (\ref{payoff}), then we can find out the Nash Equilibrium of repeated game.

@@

\section{\normalsize\textbf{Future Work}}
%Data Auction
The data auction process is a data trading mechanism and an economically-driven scheme that establishes corresponding prices of data products through bidding process between consumers and providers. While there has been many auction models\cite{BigPicDataMarket} in several areas, only a few of research focus on third-party auction platform. Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers. However, the auction process between multiple participants and analysis of potential threats are still critical issues that need to be resolved. The game theory model presented in this work, we assume each data provider's behavior is independent. However, normally there would be multiple data providers provide similar product (substitution). Only one provider is taken into considerations at present.
